A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Summarize the parsing results.

\paragraph{Parsing performance}

\todo{[Fill in some details here.}
\todo{Read report and work out what to include.}

>>>>

The full SPINN performed moderately well at reproducing the Stanford Parser's parses of the SNLI data at a transition-by-transition level with 92.4\% accuracy at test time. However, its transition prediction errors were fairly evenly distributed across sentences, and most sentences were assigned partially invalid transition sequences that either left a few words out of the final representation or incorporated a few padding tokens into the final representation.
